A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-07 paper.Rmd
small typo in top of Section 5

For clarity and consistency, the analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only on results from lineups generated with uniform fitted values, a total of `r nrow(filter(vi_survey, x_dist == "uniform"))` lineups and XXX evaluation. More evaluations were made using the uniform fitted value distribution, and it avoids potentially confounding results of the analysis by combining values from different power curves. We also expect that visual patterns are more clearly visible when the fitted value distribution is uniform. Section \ref{effect-of-fitted-value-distributions} contains comparison of the effect of fitted value distribution on power.

>>>>

For clarity and consistency, the analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only on results from lineups generated with uniform fitted values, a total of `r nrow(filter(vi_survey, x_dist == "uniform"))` lineups and XXX evaluations. More evaluations were made using the uniform fitted value distribution, and it avoids potentially confounding results of the analysis by combining values from different power curves. We also expect that visual patterns are more clearly visible when the fitted value distribution is uniform. The results in Section \ref{effect-of-fitted-value-distributions} examine the effect of fitted value distribution on power.

### 2023-04-07 paper.tex
small typo in top of Section 5

For clarity and consistency, the analysis in Sections
\ref{power-analysis}-\ref{hetero-analysis}, uses only on results from
lineups generated with uniform fitted values, a total of 4135 lineups
and XXX evaluation. More evaluations were made using the uniform fitted
value distribution, and it avoids potentially confounding results of the
analysis by combining values from different power curves. We also expect
that visual patterns are more clearly visible when the fitted value
distribution is uniform. Section
\ref{effect-of-fitted-value-distributions} contains comparison of the
effect of fitted value distribution on power.

>>>>

For clarity and consistency, the analysis in Sections
\ref{power-analysis}-\ref{hetero-analysis}, uses only on results from
lineups generated with uniform fitted values, a total of 4135 lineups
and XXX evaluations. More evaluations were made using the uniform fitted
value distribution, and it avoids potentially confounding results of the
analysis by combining values from different power curves. We also expect
that visual patterns are more clearly visible when the fitted value
distribution is uniform. The results in Section
\ref{effect-of-fitted-value-distributions} examine the effect of fitted
value distribution on power.
